%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%     \lastupdated
%    
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Eldiiar}{Dzhunusov}{ \urlstyle{same}\href{https://github.com/EldiiarDzhunusov}{ GitHub }|\href{https://www.linkedin.com/in/eldiiardzhunusov/}{ LinkedIn }|\href{https://leetcode.com/EldiiarDzhunusov/}{ LeetCode }|\href{https://codeforces.com/profile/Nullius}{ CodeForces }

\\\href{https://eldiiardzhunusov.github.io/}{ EldiiarDzhunusov.github.io }| +996778012053 |
\href{mailto:eldiiar.dzhunusov_2022@ucentralasia.org}{eldiiar.dzhunusov\_2022@ucentralasia.org}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.40\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{\href{https://ucentralasia.org/}{University of Central Asia}}\\
\descript{BS in Computer Science}
\location{Naryn, Kyrgyzstan}
\location{ Acceptance Rate: 4.3\%}
September, 2018 - Expected July, 2022\\
Member of Coding Contest Club


\sectionsep

\subsection{\href{https://70.edubishkek.kg/o-nas/}{School-gymnasium \#70 \newline
educational complex}}
\descript{Focus on Mathematics}
\location{Bishkek, Kyrgyzstan}
\location{Top 5 School in Kyrgyzstan}
Graduated in June, 2016\\








%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}


\subsection{Technical Skills}
Java \textbullet{}  Python \textbullet{}  C Language %\textbullet{} C++ 
\textbullet{} OOP
\textbullet{} Algorithms

\textbullet{} Algorithm Analysis \textbullet{} 
Git\textbullet{} Linux \textbullet{}  HTML \textbullet{} CSS \textbullet{} Bash
%\textbullet{} Docker
\textbullet{} SQL \textbullet{} Unified Modeling Language(UML)
\sectionsep

\subsection{Soft Skills}
 Team Player \textbullet{} Problem-Solving Thinking \textbullet{} Time Management \textbullet{} Flexibility \textbullet{} Public Speaking \textbullet{} Leadership \textbullet{} Trilingual Communication\\ (English, Russian, Kyrgyz)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work Experience}
\runsubsection{\href{https://ucentralasia.org/}{University of Central Asia}}
\descript{| Computer Science Teaching Assistant }
\location{October 2020 - Present | Naryn, Kyrgyzstan}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Student tutoring in the extra classes\\ in "C" programming language.
\item Code Review
\item Curriculum development for the extra classes.

\end{tightemize}
\sectionsep

\runsubsection{\href{https://hlebnasushny.ru/}{Hleb Nasushny}}
\descript{| Restaurant Attendant }
\location{June 2019 – August 2020 | Moscow, Russia}
\begin{tightemize}
\item Improved customer service by implementing a Plazius payment system.
% \item Assisted customers with food selection, inquiries and order customization requests.
\item Trained and served as a mentor for new employees.
\end{tightemize}
\sectionsep


\runsubsection{\href{http://image-cosmetika.ru/?page_id=2}{Aliyans BSM}}
\descript{| Senior Sales Manager}
\location{January 2018 – August 2018 | Bishkek, Kyrgyzstan}
\begin{tightemize}
\item Developed an ability to read individuals to identify needs and interests and adapt sales techniques accordingly.
% Google Facebook Microsoft Netflix
\item Built and led a team of motivated junior sales managers.
\end{tightemize}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.59\textwidth} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TECHNICAL PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Projects}


\runsubsection{\href{https://github.com/EldiiarDzhunusov/Minesweeper}{Minesweeper}}
\descript{| Game}
\location{November, 2020 | Bishkek, Kyrgyzstan}
\sectionsep
\begin{tightemize}
\item Built a Minesweeper game using Java language and JavaFX library.
\item Developed an algorithm  to not lose the game on the first click.
\item Increased efficiency of search by applying recursive approach.

\end{tightemize}

\sectionsep




\runsubsection{\href{https://github.com/EldiiarDzhunusov/EldiiarDzhunusov.github.io}{eldiiardzhunusov.github.io}}
\descript{| Personal Website}
\location{May, 2020 | Bishkek, Kyrgyzstan}
\begin{tightemize}
\item Built a personal website using HTML,CSS,PHP and Bootstrap.
\item Configured Back-End on Heroku server.
\item Debugged an error that was causing a slow response by 17\%.
\end{tightemize}
\sectionsep

\runsubsection{\href{https://github.com/EldiiarDzhunusov/COMP1001-Calculator}{Calculator}}
\descript{| Software}
\location{April, 2019 | Naryn, Kyrgyzstan}
\begin{tightemize}
\item Built advanced calculator using Python 3 and Tkinter, Matplotlib, and Numpy libraries.
\item Applied calculation of derivatives, area, volume, and simple math.
\item Implemented a plotting of trigonometric and polynomial functions.

\end{tightemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Object Oriented Programming\textbullet{}
Computer Systems \textbullet{}
Web Technologies \textbullet{}
Computer Architecture \textbullet{}
Calculus II \textbullet{}
Linear Algebra \textbullet{}
Digital Logical Design\textbullet{}
Software Engineering \textbullet{}
Database Management Systems \textbullet{}
Data Structure and Algorithms \textbullet{}
Discrete Mathematics \textbullet{}
Intro to Computer Science \textbullet{}
Calculus I \textbullet{}
Fundamentals of Programming 
\sectionsep


\subsection{External}



\href{https://www.coursera.org/account/accomplishments/verify/BBJ82ES293NF}{Greedy Algorithms, Minimum Spanning Trees, and
Dynamic Programming}\\
{\footnotesize \textit{\textbf{| Stanford Online}}} \\

\href{https://www.coursera.org/account/accomplishments/verify/8Y6GMJJ42MUR}{Graph Search, Shortest Paths, and Data Structures}{\footnotesize \textit{\textbf{| Stanford Online}}} \\
\href{https://www.coursera.org/account/accomplishments/verify/4HBNSGEQ6TZ4}{Shortest Paths Revisited, NP-Complete Problems
and What To Do About Them}
{\footnotesize \textit{\textbf{| Stanford Online}}} \\

\href{https://www.coursera.org/account/accomplishments/verify/9NLW95QA5L65}{Divide and Conquer, Sorting and Searching, and Randomized Algorithms} \\
{\footnotesize \textit{\textbf{| Stanford Online}}} \\

\href{https://auca.kg/en/cec_preparatorycourses/66/}{Mathematics}
{\footnotesize \textit{\textbf{| American University of Central Asia}}} \\

\href{https://www.akdn.org/our-agencies/university-central-asia/uca-pre-university-education}{Winter Upgrading Programme} 
{\footnotesize \textit{\textbf{| University of Central Asia}}} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certificates and Awards} 
\begin{tabular}{rll}

2020 & \href{https://drive.google.com/file/d/1qWr5qT-tAZjzCQhJVwCS_91mZGf8PeEm/view?usp=sharing}{Absolute Winner in Kyrgyzstan},\\& \href{https://drive.google.com/file/d/1qWr5qT-tAZjzCQhJVwCS_91mZGf8PeEm/view?usp=sharing}{Absolute Winner in the nomination "Industrial Internet"},\\
&\href{https://drive.google.com/file/d/1qWr5qT-tAZjzCQhJVwCS_91mZGf8PeEm/view?usp=sharing}{3rd/5000 Place Among all Nominations}\\
&In \href{https://olymp.digitaleconomy.world/en/}{Digital Economy International Olympiad} \space| Moscow, Russia\\
2020& ICPC Kyrgyzstan Participant\\

2019&\href{https://drive.google.com/file/d/1oHNS00dwOLS9y1tmq42F8RWxjM2WjFL0/view?usp=sharing}{Hackaton } - \href{https://dtca.kg/}{Digital Transformation in Central Asia} | Bishkek, Kyrgyzstan\\

2019& \href{https://drive.google.com/file/d/1nfR0Lww5Qxti6asNj6nNwK0REmB7b0E8/view?usp=sharing}{The Fourth Central Asian CDF Tournament}| Dushanbe, Tajikistan\\

2019& \href{https://drive.google.com/file/d/1nmrnoNYaSuMe-eunNoyV0LAmya0OgE-D/view?usp=sharing}{Model United Nations Conference} \space | Tashkent, Uzbekistan\\

2019& \href{https://drive.google.com/file/d/1o-GMVCzRXZHLrqYimTdKvgOYd2RdAMj_/view?usp=sharing}{Model United Nations Conference} \space | Khorog, Tajikistan\\

2017& \href{https://drive.google.com/file/d/1o7lv1Rfxlw0AxtvmmHWzMXZlWjPb8xUj/view?usp=sharing}{Certificate of Appreciation} by University of Central Asia\\

2016& \href{https://drive.google.com/file/d/1o5RlENDFXKvinzGZUYTIfz6aq-q7dEv1/view?usp=sharing}{Certificate of Recognition} by High School \space | Bishkek, Kyrgyzstan\\
2015& 1st place in Debate Tournament \space | Bishkek, Kyrgyzstan\\
2015& 3rd place in Teenagers in Free Enterprise(TIFE) \space | Bishkek, Kyrgyzstan\\

\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{minipage} 
\end{document}  \documentclass[]{article}
